Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2018-01-16 paper/paper.Rmd
Violin time plot and explanation added.

Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image, as a letter value plot [@letterValue]. A letter value plot is like a box plot, but more suited to skewed data like this. (Both Microsoft and Google have a few images each where they have taken a long time to complete and these were removed from this plot.) The times are quite variable between APIs, with Skybiometry being the most consistently fast. Microsoft and Animetrics are quite variable regardless of the number of faces found. Google is variable in time taken when there are few faces present, and then takes a little longer on average to find faces as the number of them in the image increases.

@@

```{r timeFigure, fig.height=6, fig.cap="System time taken by the four APIs to finish searching individual images, by number of faces discovered, displayed as a letter value plot.  Skybiometry is the most consistently fast.\\label{fig:timeFigure}"}
# 
# t1 <- ggplot(times) +  
#   geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm") + 
#   xlab("Number of faces detected") + ylab("System time (sec)") +  
#   scale_colour_manual("API", values=type.colours) + theme(legend.position = "none")

# t2 <- ggplot(times) +
#   geom_jitter(aes(x=n, y=time.sys.self, colour=type), alpha=0.2, width=0.3, height=0.01) +
#   facet_wrap(~type) +
#   ylim(c(0, 0.1)) +
#   #geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm", se=FALSE) +
#   xlab("Number of faces detected") +
#   scale_colour_manual("API", values=type.colours) + theme(legend.position = "none")

#grid.arrange(t1,t2,nrow=1)

# letter value plots
t2 <- ggplot(times, aes(as.factor(n), time.sys.self)) + 
  geom_lv(aes(fill = ..LV..)) +
  #ylim(c(0, 0.1)) + 
  facet_wrap(~type) +
  scale_y_continuous("System time (seconds)", 
    breaks=seq(0, .08, .02), limits=c(0, 0.08)) +
  # somethings funky when try to change axis labels
  xlab("Number of faces detected")

>>>>

Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image, as a violin plot. Both Microsoft and Google had few images where they had taken a significant amount of time to complete, and these were removed from this plot due to concerns regarding the network. The times taken to search are quite variable between APIs, with Skybiometry consistently spending less time than other APIs. Microsoft and Google's times vary regardless of the number of faces found.

@@

```{r timeFigure, fig.height=6, fig.cap="System time taken by the four APIs to finish searching individual images, by number of faces discovered, displayed as violins. The width of the violin shows the most common times for the group of images.\\label{fig:timeFigure}"}

# violin plot
t2 <- ggplot(times, aes(x= as.factor(n), time.sys.self)) +
  geom_violin(scale = "width") + ylim(0,0.08) +
  #geom_jitter(height = 0.005, width = 0.1, alpha=0.5) +
  facet_wrap(~ type) +
  xlab("Amount of faces found") +
  ylab("Time taken per image (Seconds)")
